---
title: "shiny project"
author: "Nozhat Ghazi"
date: "25-12-2018"
output:
  beamer_presentation: default
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



## How to use the application

Using the data provided by ChickWeight dataset,a linear model fitted to predict a chicken's weight based on the time and diet.

The application is running on (https://vardnoosh.shinyapps.io/shiny/)

ui.R, and Server.R Code in my github repository (https://github.com/vardnoosh/Shiny-Application-and-Reproducible-Pitch/tree/gh-pages)

## ChickWeight Dataset

The data used in the app comes from the ChickWeight dataset. 

```{r summary, echo=FALSE}
data("ChickWeight")
dt <- ChickWeight[ChickWeight$Diet == c("1","2"),]
summary(dt)
```

## Plot
In the scatterplot below are represented the data used for the prediction model
```{r plot , echo=FALSE}

data("ChickWeight")
plot(jitter(dt$weight) ~ dt$Time,xlab="Time",ylab="Weight of the Chicken(gm)",main="Scatterplot of ChickWeight Data",pch=19,frame.plot=FALSE,col=ifelse(dt$Diet=="1","2", "pink"))
legend(65,80,pch=c(19,19),col=c("pink","light blue"),c("1", "2"),bty="o",cex=.8)
```